Effective parameters of ferroelectric dielectric mixtures

### 2019-06-11 paper/arxiv/response_letter.tex

\rep{It has been clarified in the abstract and introduction that this is a computational and numerical study.}

\item In the introduction, please outline the actual ferroelectric composites in common use in this field.
 It is useful to know what materials this method can be used to model.

\item In the introduction: Local field engineering and field amplification has become more and more useful
 at other frequency ranges, especially in the THz and near-IR, to control the properties of other materials
  (eg. \href{https://doi.org/10.3390/photonics6010022}{Photonics 2019, 6(1), 22}). Could the authors expand
   on some other systems, besides ferro-electric metamaterials, that this method might apply to. For
    instance maybe tunable
    \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.110.217404}{GaAs meta-devices}.

    \rep{We have expanded on this point in the introduction and added possible applications of the model and corresponding references.}

@@

\item In the introduction: The authors mention that there are generally limitations to the current
 numerical and theoretical models used in the field, but do not go into any detail. Could the authors
  expand on this point? What are the limitations?

\item Theory Section, A. In figure 1, are these electrostatics measurements performed by the authors? It is
 unclear based on the figure and surrounding paragraphs. I assume they are as no citation is provided for
  the data. Could the authors discuss the details of how these measurements were made? This would be useful
   for metamaterials researchers who do not work in this frequency range.

\rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A.}

@@

\end{itemize}

% ~\\
\subsection{Remarks to author(s)}

  The paper is interesting and can be published with very small revisions.

  \begin{enumerate}
  \item Although composites are engineered materials, in my opinion, we cannot call "metamaterial" a
   composite if we do not demonstrate specific frequency-dependent behavior and if the regular repeated
    units characteristic to the metamaterial are not smaller than the corresponding wavelength where we
     found the mentioned property. In this paper there is not an analysis vs frequency of the properties,
      so that your material is a di-phase composite. I suggest to change the title.

\rep{The title has been changed to \textit{Enhanced tunability in ferroelectric composites through local field
enhancement and the effect of disorder}}

  \item You gave experimental data for BST ceramics that were used to derive Landau coefficients. It is
   necessary to give some details of the sample (composition?) and measurements or to cite an experimental
    work.

    \rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A.}

  \item You may compare the results of your simulations with the results of other studies.

### 2019-06-11 paper/arxiv/marked_manuscript.tex
correc paper

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
 We investigate \co{numerically} the homogenized permittivities of metamaterials made of low index dielectric inclusions in a ferroelectric matrix under
 a static electric field. A refined model is used to take into account the coupling
 between the electrostatic problem and the electric field dependent permittivity of the
 ferroelectric material, leading to a local field enhancement and permittivity change in the ferroelectric.
 Periodic and pseudo-random structures in two dimensions are investigated and
 we \co{compute} the effective permittivity, losses, electrically induced anisotropy and tunability
 of those metamaterials. We show that the tunability of such composites might be substantially
 enhanced in the periodic case, \co{whereas} introducing disorder in the microstructure
 weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel composite ceramics with improved characteristics for controllable microwave devices.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 \section{Introduction}
 Ferroelectric materials play a crucial role in reconfigurable
 microwave devices, with typical applications including antenna beam steering,
 phase shifters, tunable power splitters, filters, voltage controlled oscillators and
 matching networks \cite{tagantsev_ferroelectric_2018}. Both bulk ceramics and thin films have
 been employed to design frequency agile components \cite{vendik_ferroelectric_1999,
 lancaster_thin-film_1998,xi_oxide_2000} and metamaterials \cite{hand_frequency_2008, zhao_experimental_2008}.
 The main reason of using
 ferroelectric materials is their strong dependence of their permittivity $\varepsilon$
 on an applied electric field $E$, which is measured by their tunability defined as $n = \varepsilon(0)/\varepsilon(E)$,
 along with a non hysteresis behaviour when used in their paraelectric state.
 The key requirements for antenna and microwave applications are large tunability and low losses.
 These two characteristics are correlated and one has to find a trade-off for optimal
  device performance, which can be quantified by the so called commutation quality factor
 $K = (n -1)^2/(n\, \tan\delta(0)\,\tan\delta(E))$, where $\tan\delta$ is the loss tangent.\\
 These materials have usually high permittivity values even at microwave frequencies,
 often leading to slow response time and impedance mismatch, which can be an issue in some practical
 applications. Thus it has been considered to mix ferroelectric \co{ceramics with} low-index and
 low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
 use porous ceramics to achieve the same goals without unwanted chemical reactions at the boundaries between dissimilar materials.
The effective parameters of those composites have been investigated
\cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003}
and it has been found that the permittivity can be greatly reduced while losses are much less
 sensitive to the dielectric phase addition, and in some situations lead to a small
  increase of the tunability of the mixtures. Analytical models based on the Bruggeman effective
medium approach for low concentration of dielectrics were derived for different configurations (columnar, layered and spherical
inclusions models) and have been successfully compared with numerical simulations and experiments \cite{sherman_ferroelectric-dielectric_2006}.
  In the context of porous ferroelectrics,
   the homogenized properties strongly depends on the size and morphology of the pores
    \cite{okazaki_effects_1973,stanculescu_study_2015}.
    Recently, the concept of tailoring the nonlinear properties of ferroelectric
     and dielectric structures by local field engineering has been introduced \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012,cazacu_tunable_2013}.
      It was shown through finite element calculation including the nonlinear coupling, that by employing
      composite materials made of linear dielectric inclusions into a ferroelectric matrix, one can lower the permittivity while maintaining
      high tunability, due to the local field in the ferroelectric phase which is tuned by the linear dielectric phase.
Moreover, the effect of grain sizes in ferroelectric
ceramics was studied using a model taking the field enhancement into account at
the grain boundaries, and the predicted behaviour successfully compared to experimental data \cite{padurariu_field-dependent_2012}.
Generally, there is a need for refined theoretical and numerical models to explain and design
tunable materials and composites with tailored nonlinear properties.
\\
This study investigates \co{numerically} the effective permittivity of composites made of
 dielectric inclusions in a ferroelectric matrix
by using a two-scale convergence method \cite{allaire_homogenization_1992,
 guenneau_homogenization_2000}.
The originality lies in the fact that a fully coupling model is employed to
calculate the electrostatic field distribution when a uniform biasing field is
applied on the structures, which will result in a local modification of the permittivity
in the ferroelectric phase due to the microstructure. As compared to a simple uncoupled model where the
ferroelectric phase is only modified through the biasing field,
the resulting effective permittivity, dielectric losses, tunability and
anisotropy significantly differ. \co{In contrast with} earlier sudies in the
\co{literature} \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
the non-linear coupling beyond the first iteration and use two-scale
convergence homogenization analysis to obtain the effective parameters at
higher frequencies, instead of a capacitance-based model.
\co{The model we developed has been implemented with the finite element method (FEM)
and we realise a systematic computational study of ferroelecric-dielectric mixtures.
First, we consider} metamaterials consisting of a square array of parallel
dielectric rods with circular cross section in a ferroelectric host, and
then investigate the effect of random distribution of those rods within the unit cell.

@@

\section{Numerical results}
In the following numerical results, the dielectric phase is supposed to be
lossless and non dispersive with $\epsd = 3$ while the ferroelectric material follows the
permittivity described in section~\ref{permmodel} and has a constant loss
tangent $\tan \delta^{\rm f} = 10^{-2}$.
Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
Method using the open source packages Gmsh \cite{geuzaine_gmsh:_2009} and GetDP \cite{dular_general_1998}.
In both cases we use a square unit cell $\Omega$ of length $d$ with periodic boundary
conditions along $x$ and $y$. Second order Lagrange elements are used and the
solution is computed with a direct solver (MUMPS \cite{amestoy_fully_2001}).
% The source code and
% data necessary to reproduce the results reported in this paper are freely available
% online.

@@

We have studied the homogenized properties of dielectric/ferroelectric mixtures
using a rigorous model that take into account the coupling between the electrostatic
field distribution and the field dependant ferroelectric permittivity tensor. After
convergence of the coupled problem, the effective permittivity tensor is calculated using
two scale convergence homogenization theory.
The results obtained by this model differ significantly from a simple assumption that
the permittivity of the ferroelectric respond just to the uniform biasing field.
We have considered both periodic and random arrays
of dielectric rods in a ferroelectric matrix in 2D, and studied their effective properties
for TM polarization as a function of dielectric concentration and bias field.
Importantly, adding more low index and low loss dielectric allows to decrease
the overall permittivity significantly and slightly lower the losses.
For the periodic case, the tunability is higher than the bulk due to local field enhancement, whereas
this effect is strongly suppressed when disorder is introduced. The asymmetric redistribution of the permittivity
induce an effective anisotropy that is added to the one arising purely from the ferroelectric material.
The properties of the composites are affected by multiple factors:
geometry and the spatially dependent electric field that will induce locally a tunable, anisotropic
response in the ferroelectric phase depending on its amplitude and direction.
This suggest that the performances of the composites
may be enhanced by distributing the two phases in an optimal way to get high
tunability and low losses. Further work in that direction is needed as well as
extending this study to 3D media.
Finally, because the permittivity of the dielectric is much smaller than the ferroelectric one,
it would be of great interest to use high contrast homogenization theory
\cite{bouchitte_homogenization_2004, cherednichenko_homogenization_2015} to
study this kind of mixtures.
This would reveal the frequency dependant artificial magnetism due to "micro-resonances"
in the high index phase and potentially lead to composites with tunable effective permeability.\\
To finish, the general method followed by this model could be applied to other type of tunable
systems including for example ferromagnetic materials, liquid crystals, or
 field-enhanced carrier dynamics in doped semiconductors
\cite{keiser_terahertz_2019}
\cite{fan_nonlinear_2013}

\begin{acknowledgments}
This work was funded by the Engineering and Physical Sciences Research
Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
Electromagnetics and Materials Modelling to Bridge the Gap between
Design and Manufacturing (AOTOMAT)'.\\
The authors would like to thanks Henry Giddens for performing the
measurements of ferroelectric permittivity used in this paper.\\
%
% Benjamin Vial wrote devised the research, implemented
% the codes and wrote the paper. Yang Hao supervised the research and
% co-authored the manuscript.\\
% The authors declare no competing interrests.\\
The codes necessary to reproduce the results in this article are freely
available online at this address: \href{https://www.github.com/benvial/ferromtm}{https://www.github.com/benvial/ferromtm}.
\end{acknowledgments}

>>>>

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
 We investigate \co{numerically} the homogenized permittivities of \co{composites} made of low index dielectric inclusions in a ferroelectric matrix under
 a static electric field. A refined model is used to take into account the coupling
 between the electrostatic problem and the electric field dependent permittivity of the
 ferroelectric material, leading to a local field enhancement and permittivity change in the ferroelectric.
 Periodic and pseudo-random structures in two dimensions are investigated and
 we \co{compute} the effective permittivity, losses, electrically induced anisotropy and tunability
 of those metamaterials. We show that the tunability of such composites might be substantially
 enhanced in the periodic case, \co{whereas} introducing disorder in the microstructure
 weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel composite ceramics with improved characteristics for controllable microwave devices.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 \section{Introduction}
 Ferroelectric materials play a crucial role in reconfigurable
 microwave devices, with typical applications including antenna beam steering,
 phase shifters, tunable power splitters, filters, voltage controlled oscillators and
 matching networks \cite{tagantsev_ferroelectric_2018}. Both bulk ceramics and thin films have
 been employed to design frequency agile components \cite{vendik_ferroelectric_1999,
 lancaster_thin-film_1998,xi_oxide_2000} and metamaterials \cite{hand_frequency_2008, zhao_experimental_2008}.
 The main reason of using
 ferroelectric materials is their strong dependence of their permittivity $\varepsilon$
 on an applied electric field $E$, which is measured by their tunability defined as $n = \varepsilon(0)/\varepsilon(E)$,
 along with a non hysteresis behaviour when used in their paraelectric state.
 The key requirements for antenna and microwave applications are large tunability and low losses.
 These two characteristics are correlated and one has to find a trade-off for optimal
  device performance, which can be quantified by the so called commutation quality factor
 $K = (n -1)^2/(n\, \tan\delta(0)\,\tan\delta(E))$, where $\tan\delta$ is the loss tangent. 
 These materials have usually high permittivity values even at microwave frequencies,
 often leading to slow response time and impedance mismatch, which can be an issue in some practical
 applications. Thus it has been considered to mix ferroelectric \co{ceramics with} low-index and
 low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
 use porous ceramics to achieve the same goals without unwanted chemical reactions at the boundaries between dissimilar materials. \co{In particular, the addition of magnesium oxide in barium strontium titanate (BST) ceramics have been shown to decrease the losses while keeping good tunability \cite{irvin_three-dimensional_2005,chung_low-losses_2008}. Ceramics
 such as $\rm Pb(Zr,Ti)O_3$ (PZT) and $\rm BaTiO_3$ (BT) have been used as fillers in polymer
 based composites with high dielectric constant \cite{wang_piezoelectric_2012}. Other mixtures include metal–polymer composites \cite{li_ferroelectric_2013}
 and electroactive polymers such as poly(vinylidene fluoride) (PVDF) with high index dielectric inclusions \cite{hu_preparation_2015}.
 }

The effective parameters of those composites have been investigated
\cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003}
and it has been found that the permittivity can be greatly reduced while losses are much less
 sensitive to the dielectric phase addition, and in some situations lead to a small
  increase of the tunability of the mixtures. Analytical models based on the Bruggeman effective
medium approach for low concentration of dielectrics were derived for different configurations (columnar, layered and spherical
inclusions models) and have been successfully compared with numerical simulations and experiments \cite{sherman_ferroelectric-dielectric_2006}.
  In the context of porous ferroelectrics,
   the homogenized properties strongly depends on the size and morphology of the pores
    \cite{okazaki_effects_1973,stanculescu_study_2015}.
    Recently, the concept of tailoring the nonlinear properties of ferroelectric
     and dielectric structures by local field engineering has been introduced \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012,cazacu_tunable_2013}.
      It was shown through finite element calculation including the nonlinear coupling, that by employing
      composite materials made of linear dielectric inclusions into a ferroelectric matrix, one can lower the permittivity while maintaining
      high tunability, due to the local field in the ferroelectric phase which is tuned by the linear dielectric phase.
Moreover, the effect of grain sizes in ferroelectric
ceramics was studied using a model taking the field enhancement into account at
the grain boundaries, and the predicted behaviour successfully compared to experimental data \cite{padurariu_field-dependent_2012}.
Generally, there is a need for refined theoretical and numerical models to explain and design
tunable materials and composites with tailored nonlinear properties.
\co{Note that the general method followed by our coupled model could be applied to other type of tunable
systems where local field enhancement and amplification is relevant, including for example ferromagnetic metamaterials \cite{carignan_ferromagnetic_2011}, liquid crystals based devices \cite{werner_liquid_2007}, or field-enhanced carrier dynamics in doped semiconductors at other frequency ranges, particularly in the THz and near-infrared
\cite{keiser_terahertz_2019, fan_nonlinear_2013}.
}

This study investigates \co{numerically} the effective permittivity of composites made of
 dielectric inclusions in a ferroelectric matrix
by using a two-scale convergence method \cite{allaire_homogenization_1992,
 guenneau_homogenization_2000}.
The originality lies in the fact that a fully coupling model is employed to
calculate the electrostatic field distribution when a uniform biasing field is
applied on the structures, which will result in a local modification of the permittivity
in the ferroelectric phase due to the microstructure. As compared to a simple uncoupled model where the
ferroelectric phase is only modified through the biasing field,
the resulting effective permittivity, dielectric losses, tunability and
anisotropy significantly differ. \co{In contrast with} earlier studies in the
\co{literature} \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
the non-linear coupling beyond the first iteration and use two-scale
convergence homogenization analysis to obtain the effective parameters at
higher frequencies, instead of a capacitance-based model.
\co{The model we developed has been implemented with the finite element method (FEM)
and we realise a systematic computational study of ferroelecric-dielectric mixtures.
First, we consider} metamaterials consisting of a square array of parallel
dielectric rods with circular cross section in a ferroelectric host, and
then investigate the effect of random distribution of those rods within the unit cell.

@@

\section{Numerical results}
In the following numerical results, the dielectric phase is supposed to be
lossless and non dispersive with $\epsd = 3$ while the ferroelectric material follows the
permittivity described in section~\ref{permmodel} and has a constant loss
tangent $\tan \delta^{\rm f} = 10^{-2}$.
Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
Method using the open source packages Gmsh \cite{geuzaine_gmsh_2009} and GetDP \cite{dular_general_1998}.
In both cases we use a square unit cell $\Omega$ of length $d$ with periodic boundary
conditions along $x$ and $y$. Second order Lagrange elements are used and the
solution is computed with a direct solver (MUMPS \cite{amestoy_fully_2001}).
% The source code and
% data necessary to reproduce the results reported in this paper are freely available
% online.

@@

We have studied the homogenized properties of dielectric/ferroelectric mixtures
using a rigorous model that take into account the coupling between the electrostatic
field distribution and the field dependant ferroelectric permittivity tensor. After
convergence of the coupled problem, the effective permittivity tensor is calculated using
two scale convergence homogenization theory.
The results obtained by this model differ significantly from a simple assumption that
the permittivity of the ferroelectric respond just to the uniform biasing field.
We have considered both periodic and random arrays
of dielectric rods in a ferroelectric matrix in 2D, and studied their effective properties
for TM polarization as a function of dielectric concentration and bias field.
Importantly, adding more low index and low loss dielectric allows to decrease
the overall permittivity significantly and slightly lower the losses.
For the periodic case, the tunability is higher than the bulk due to local field enhancement, whereas
this effect is strongly suppressed when disorder is introduced. The asymmetric redistribution of the permittivity
induce an effective anisotropy that is added to the one arising purely from the ferroelectric material.
The properties of the composites are affected by multiple factors:
geometry and the spatially dependent electric field that will induce locally a tunable, anisotropic
response in the ferroelectric phase depending on its amplitude and direction.
This suggest that the performances of the composites
may be enhanced by distributing the two phases in an optimal way to get high
tunability and low losses. Further work in that direction is needed as well as
extending this study to 3D media.
Finally, because the permittivity of the dielectric is much smaller than the ferroelectric one,
it would be of great interest to use high contrast homogenization theory
\cite{bouchitte_homogenization_2004, cherednichenko_homogenization_2015} to
study this kind of mixtures.
This would reveal the frequency dependant artificial magnetism due to "micro-resonances"
in the high index phase and potentially lead to composites with tunable effective permeability.\\

\begin{acknowledgments}
This work was funded by the Engineering and Physical Sciences Research
Council (EPSRC), UK, under a grant (EP/P005578/1) "Adaptive Tools for
Electromagnetics and Materials Modelling to Bridge the Gap between
Design and Manufacturing (AOTOMAT)".\\
The authors would like to thanks Henry Giddens for performing the
measurements of ferroelectric permittivity used in this paper.\\
%
% Benjamin Vial wrote devised the research, implemented
% the codes and wrote the paper. Yang Hao supervised the research and
% co-authored the manuscript.\\
% The authors declare no competing interrests.\\
The codes necessary to reproduce the results in this article are freely
available online at this address: \href{https://www.github.com/benvial/ferromtm}{https://www.github.com/benvial/ferromtm}.
\end{acknowledgments}

### 2019-06-11 poster/main_poster.tex
correc paper

  \begin{column}{.48\columnwidth}
    Metamaterials consisting of periodic and random arrays of rods
      are considered for transverse electric polarization case
      and we study their effective permittivity, losses, electrically induced anisotropy
      and tunability by a two scale convergence homogenization method.
  \end{column}

@@

%%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(2.5cm,22.5cm)
  \begin{posterblock}{Context}{benchcolor1}
    Ferroelectric materials play a crucial role in reconfigurable
    microwave devices, with typical applications including antenna beam steering,
    phase shifters, tunable power splitters, filters, voltage controlled oscillators and
    matching networks \cite{tagantsev_ferroelectric_2018}, and the key requirements are large tunability and low losses.
     These materials have high permittivity values even at microwave frequencies, which can be an issue in some practical
     applications. Thus it has been considered to mix ferroelectrics to low-index and
     low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
     use porous ceramics \cite{sherman_ferroelectric-dielectric_2006,padurariu_tailoring_2012}.

@@

\begin{column}{.64\columnwidth}
  \mysubtitle{Homogenization}
  Two scale convergence homogenization \cite{allaire_homogenization_1992, guenneau_homogenization_2000}, TE case:
  solutions $\psi_j$ of two annex problems
  % $\mathcal P_j$, $j=\{1, 2\}$:
  \begin{equation}
   \div \left[ \xitens \grad(\psi_j + r_j) \right] = 0,
   \label{eq_hom_annex}
  \end{equation}
  where $\B r = (x, y)^{\rm T}$ and $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
  The homogenized tensor $\xihom$ is obtained with:
  \begin{equation}
   \xihom = \langle \xitens \rangle + \B \phi,
   \label{eq_hom}
  \end{equation}
  where $\langle . \rangle$ denotes the mean value over the unit cell.
  Correction terms $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.\\
\end{column}

@@

\mysubtitle{Open source numerical implementation}
Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
Method using the freewares Gmsh \cite{geuzaine_gmsh:_2009} and GetDP \cite{dular_general_1998} driven by a Python package.

@@

%%%%%%%%%%%%%%%%%%%%%  Acknowledgments box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(43.5cm,105.cm)
\myblocktitle{Acknowledgments}{fresnelgreenblue}
\color{fresnelblack}
This work was funded by the Engineering and Physical Sciences Research
Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
Electromagnetics and Materials Modelling to Bridge the Gap between
Design and Manufacturing (AOTOMAT)'
\end{textblock*}
%

>>>>

  \begin{column}{.48\columnwidth}
    Metamaterials consisting of periodic and random arrays of rods
      are considered for the transverse electric polarization case
      and we study their effective permittivity, losses, electrically induced anisotropy
      and tunability by a two scale convergence homogenization method.
  \end{column}

@@

%%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(2.5cm,22.5cm)
  \begin{posterblock}{Context}{benchcolor1}
    Ferroelectric materials play a crucial role in reconfigurable
    microwave devices, with typical applications including antenna beam steering,
    phase shifters, tunable power splitters, filters, voltage controlled oscillators and
    matching networks \cite{tagantsev_ferroelectric_2018}, and the key requirements are large tunability and low losses.
     These materials have high permittivity values even at microwave frequencies, which can be an issue in some practical
     applications. Thus it has been considered to mix ferroelectrics with low-index and
     low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
     use porous ceramics \cite{sherman_ferroelectric-dielectric_2006,padurariu_tailoring_2012}.

@@

\begin{column}{.64\columnwidth}
  \mysubtitle{Homogenization}
  Two scale convergence homogenization \cite{allaire_homogenization_1992, guenneau_homogenization_2000}, TE case:
  solutions $\psi_j$ of two annex problems $\mathcal P_j$, $j=\{1, 2\}$:
  \begin{equation}
   \div \left[ \xitens \grad(\psi_j + r_j) \right] = 0,
   \label{eq_hom_annex}
  \end{equation}
  where $\B r = (x, y)^{\rm T}$ and $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.\\
  The homogenized tensor $\xihom$ is obtained with:
  \begin{equation}
   \xihom = \langle \xitens \rangle + \B \phi,
   \label{eq_hom}
  \end{equation}
  where $\langle . \rangle$ denotes the mean value over the unit cell.
  Correction terms $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.\\
\end{column}

@@

\mysubtitle{Open source numerical implementation}
Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
Method using the libre software Gmsh \cite{geuzaine_gmsh_2009} and GetDP \cite{dular_general_1998} driven by a Python package.

@@

%%%%%%%%%%%%%%%%%%%%%  Acknowledgments box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(43.5cm,105.cm)
\myblocktitle{Acknowledgments}{fresnelgreenblue}
\color{fresnelblack}
This work was funded by the Engineering and Physical Sciences Research
Council (EPSRC), UK, under a grant (EP/P005578/1) \textit{"Adaptive Tools for
Electromagnetics and Materials Modelling to Bridge the Gap between
Design and Manufacturing (AOTOMAT)"}
\end{textblock*}
%
